### 2020-11-20 Thesis-Chapter2-Background.tex
Address review feedback

There are two major cryptographic protocol families, symmetric and asymmetric. In \ac{sym-crypto}, which was discovered
long ago, encryption and decryption are performed with the same key, and both parties must have this key in order to
communicate securely. In \ac{asym-crypto}, which was discovered recently and is also called \ac{public-key-crypto},
encryption and decryption are performed with two paired keys, called the public key and the private key. The innovation
of \ac{public-key-crypto} is that the public key is not secret, and using this technique, two parties can communicate
securely without requiring a previously agreed upon shared secret.

@@

Cryptography is the technical foundation for many forms of computer and network security. Security is defined in terms
of several properties: authentication, integrity, non-repudiation, confidentiality, availability, and authorization
\cite{shostack_threat_2014}. These system-level properties emerge from both the composition of the system's components
(architecture) and the security of the components themselves; likewise, the security of each component emerges from the
architecture of its subcomponents and the security of the subcompenents themselves. At the end of this chain of
analysis, the security of primitive components commonly relies on cryptography.

@@

% NOTE: tried to find examples of high profile bugs or hacks that relied on crypto failures, but most are still
% architectural (exposed databases, default credentials (Mirai botnet)), human (BEC), or insecure code (buffer
% overflows--key to EternalBlue (wannacry and notpetya) and MS08-067 (Conficker)).

@@

Computerized encryption is a new technology, but the field of cryptography is old, since demand for privacy is as old as
communication itself. The most well known ancient example of rudimentary encryption is the Caesar cipher, named after
the character transposition technique Julius Caesar used to protect private correspondence
\cite{luciano_cryptology_1987}. Significant developments include the first formal cryptographic study by Arab scholars
in the eighth century, advancements made out of necessity in the twentieth century's world wars, and the application of
computers to cryptographic problems \cite{kahn_codebreakers_1996}. Claude Shannon's formalized the modern ``mathematical
analysis of cryptography'' in 1949 \cite{shannon_communication_1949}, and Whitfield Diffie and Martin Hellman published
research on \ac{public-key-crypto} in 1976 \cite{diffie_new_1976}. The discovery of \ac{public-key-crypto} was an
important advance. Combined with computer networking and personal computing advances in the 1980s, it for the first time
put the power of strong encryption not just in the hands of governments and militaries, but of ordinary people.

@@

\paragraph*{Volatile Politics} Finally, \ac{the-cw2} is taking place amongst a political landscape marked by
uncertainty, extremism, misinformation, and most recently, a pandemic that will have unknown impacts. Since legislature
is part of the broader data security threat model, its behavior is important. Unfortunately, the dynamics of present
leadership and the lack of reliable data on what law enforcement agencies need make it difficult for the technical
community to engage productively with policy makers \cite{granick_2018}.

@@

\newcommand{\lawsstart}{\begin{itemize}}
\newcommand{\law}[4]{ % Year, name, citation, description
    \item #1: \textbf{#2} \cite{#3} \nopagebreak

@@

    \law{1789}{\acf{AWA}}{congress_1789}{

@@

    \law{1791}{Bill of Rights: Amendments I, IV, and V}{madison_1791}{

@@

    \law{1976}{\acf{AECA}}{morgan_hr13680_1976}{

@@

    \law{1978}{\acf{FISA}}{rodino_1978}{

@@

%     \law{1986}{\acf{CFAA}}{hughes_hr4718_1986}{
% Criminalized ``knowingly access[ing] a computer without authorization or exceeding authorized access'' and thereby
% violating the confidentiality, integrity, or availability of the system. While presumably intended to target hacking,
% the \acs{CFAA} has been used to prosecute a host of crimes, and suffers from dated language;
% % ---what does it mean to ``access'' a ``computer'' loading a simple webpage may involve dozens of devices---
% whether violating the terms of service constitutes ``exceeding authorized access'' remains an open question
% \cite{wolff_computer_2016}. Importantly for \ac{EA}, the law includes carve-outs for law enforcement and intelligence
% activities.
%
% Follow up: CFAA going before supreme court: https://www.cyberscoop.com/cfaa-will-soon-day-supreme-court/
% }

    \law{1986}{\acf{ECPA}}{kastenmeier_hr4952_1986}{

@@

    \law{1994}{\acf{CALEA}}{edwards_hr4922_1994}{

@@

    \law{2001}{\ac{USAPATRIOTAct}}{sensenbrenner_2001}{

@@

%     \law{2007}{\acf{PAA}}{mcconnell_s1927_2007}{
% Retroactively approved of GWB's warrantless wiretapping policy, a loose interpretation of FISA
% \cite{landau_making_2013}.
% }

    \law{2008}{\acf{FISAAA}}{reyes_hr6304_2008}{

@@

    \law{2015}{\ac{USAFREEDOMAct}}{sensenbrenner_2015}{

@@

    \law{1993}{The \ac{clipperchip}}{press_1993}{

@@

    \law{1996}{The \acf{SAFEAct}}{goodlatte_hr3011_1996}{

@@

    \law{1996}{The \acf{PROCODEAct}}{burns_s1726_1996}{

@@

%     \law{1997}{Encrypted Communications Privacy Act}{leahy_s376_1997}{
% % mix of SE protection and EA guidelines?
% }

%     \law{1998}{Encryption Protects the Rights of Individuals from Violation and Abuse in CYberspace (E-PRIVACY) Act}
%         {ashcroft_s2067_1998}{
% % like above?
% }

%     \law{1999}{Encryption for the National Interest Act}{goss_hr2616_1999}{
% }

%     \law{1999}{Tax Relief for Responsible Encryption Act}{goss_hr2617_1999}{
% % ^^ these two introduced by same rep on same day
% }

    \law{1999}{\ac{CESA}}{administration_CESA_1999}{

@@

    \law{2000}{Enhancement of Privacy and Public Safety in Cyberspace Act}{leahy_s3083_2000}{

@@

    \law{2016}{Compliance with Court Orders Act (discussion draft)}{burr_2016}{

@@

    \law{2018}{The Secure Data Act}{lofgren_hr5823_2018}{

@@

    \law{2019}{The \ac{ENCRYPTAct}}{lieu_hr4170_2019}{

@@

    \law{2020}{The \acf{EARNITAct}}{graham_s3398_2020}{

@@

    \law{2020}{The \acf{LEADAct}}{graham_2020}{

@@

% IDEA: put this in an appendix too? Or its own chapter? Too much detail for the background section.
%
% For more, read donahue_comparative_2018 (Israel and China) and budish_encryption_2018 (framework for analysis)
%
% Since the enactment of the Regulation of Investigatory Powers Act 2000, the U.K. government had the ability to serve
% written notices requiring mandated decryption. Law enforcement and intelligence agencies also have explicit permission
% to perform ``computer network exploitation,'' and approach this thesis refers to as ``\ac{lawful-hacking}.'' 2016's
% Investigatory Powers Act expanded these capabilities and, among other additions, in section 253 created ``technical
% capability notices'' that the Secretary of State can issue to telecommunications operators mandating \ac{EA}
% \cite{legislature_2016}.

@@

% There are several types of approaches:
% IDEA: my selections here are also rather sparse. Create another appendix? (I love work). Possibly create table of
% properties below, similar to denning_taxonomy_1996. savage_lawful_2018 has some good citations to mine.
% - Allow strong encryption (anyone with the users' private keys can see it)
% - Disallow encryption (anyone can see it)
% - Make encryption sufficiently weak, e.g. limit key length (anyone with enough CPU can see it)
% - Require use of backdoored algorithms, security via obscurity (anyone with the secret knowledge can see it)
% - Allow any encryption, just be able to provide keys (anyone with the extra keys can see it)
%   - Store extra in gov't DBs, in corporate DBs, in third-party DBs, on blockchain, in secure HW on device
%   - Split the key and store it multiple places
%   - See denning_taxonomy_1996
% - Use some alternative path
%   - Coerced passwords, finding unencrypted copies, seizing devices while unlocked, lawful hacking

@@

% Moving forward, what are the elements that are needed for a feasible EA system? (1) White-box-secure ways of producing
% key recovery information. Do the protocols exist? EES failed. Needs to be rock solid. (2) Dispersed key recovery
% information. (3) A robust, antifragile, inherently secure means of protecting those keys, and perhaps decaying them over
% time (https://en.wikipedia.org/wiki/Data_degradation).

@@

\subsection{Non-Escrow Cryptographic Recovery}

@@

% these look good: sacharoff_unlocking_2018, fredona_fifth_2016
% this probably has something to say: kerr_encryption_2017

@@

@@

% IDEA:
% Use the slightly more complete IBIS notation, which includes ISSUES and POSITIONS as well as ARGUMENTS.
% (Argdown) basically just has arguments and positions. The additional types may make the total picture clearer.
% Either use styling with #hashtags (https://argdown.org/syntax/#hashtags with
%                                    https://argdown.org/guide/colorizing-maps.html#the-colorscheme-setting)
% Or add a plugin (https://argdown.org/guide/extending-argdown.html)

>>>>

There are two major cryptographic protocol families, symmetric and asymmetric. In \ac{sym-crypto}, which was invented
long ago, encryption and decryption are performed with the same key, and both parties must have this key in order to
communicate securely. In \ac{asym-crypto}, which was invented recently and is also called \ac{public-key-crypto},
encryption and decryption are performed with two paired keys, called the public key and the private key. The innovation
of \ac{public-key-crypto} is that the public key is not secret, and using this technique, two parties can communicate
securely without requiring a previously agreed upon shared secret.

@@

Cryptography is the technical foundation for many forms of computer and network security. Security is defined in terms
of several properties: authentication, integrity, non-repudiation, confidentiality, availability, and authorization
\cite{shostack_threat_2014}. These system-level properties emerge from both the composition of the system's components
(architecture) and the security of the components themselves; likewise, the security of each component emerges from the
architecture of its subcomponents and the security of the subcomponents themselves. At the end of this chain of
analysis, the security of primitive components commonly relies on cryptography.

@@

% I tried to find examples of high profile bugs or hacks that relied on crypto failures, but most are still
% architectural (exposed databases, default credentials (Mirai botnet)), human (BEC), or insecure code (buffer
% overflows--key to EternalBlue (wannacry and notpetya) and MS08-067 (Conficker)).

@@

Computerized encryption is a new technology, but the field of cryptography is old, since demand for privacy is as old as
communication itself. The most well known ancient example of rudimentary encryption is the Caesar cipher, named after
the character substitution technique Julius Caesar used to protect private correspondence
\cite{luciano_cryptology_1987}. Significant developments include the first formal cryptographic study by Arab scholars
in the eighth century, advancements made out of necessity in the twentieth century's world wars, and the application of
computers to cryptographic problems \cite{kahn_codebreakers_1996}. Claude Shannon's formalized the modern ``mathematical
analysis of cryptography'' in 1949 \cite{shannon_communication_1949}, and Whitfield Diffie and Martin Hellman published
research on \ac{public-key-crypto} in 1976 \cite{diffie_new_1976}. The discovery of \ac{public-key-crypto} was an
important advance. Combined with computer networking and personal computing advances in the 1980s, it for the first time
put the power of strong encryption not just in the hands of governments and militaries, but of ordinary people.

@@

\paragraph*{Volatile Politics} Finally, \ac{the-cw2} is taking place amongst a political landscape marked by
uncertainty, extremism, misinformation, and a pandemic that will have unknown long-term  impacts. Since legislature is
part of the broader data security threat model, its behavior is important. Unfortunately, the dynamics of present
leadership and the lack of reliable data on what law enforcement agencies need make it difficult for the technical
community to engage productively with policy makers \cite{granick_2018}.

@@

\newcommand{\lawsstart}{\begin{itemize}}
\newcommand{\law}[4]{ % Year, name, citation, description
    \item #1: \textbf{#2} #3 \nopagebreak

@@

    \law{1789}{\acf{AWA}}{\cite{congress_1789}}{

@@

    \law{1791}{Bill of Rights: Amendments I, IV, and V}{\cite{madison_1791}}{

@@

    \law{1976}{\acf{AECA}}{\cite{morgan_hr13680_1976}}{

@@

    \law{1978}{\acf{FISA}}{\cite{rodino_1978}}{

@@

%     \law{1986}{\acf{CFAA}}{\cite{hughes_hr4718_1986}}{
% Criminalized ``knowingly access[ing] a computer without authorization or exceeding authorized access'' and thereby
% violating the confidentiality, integrity, or availability of the system. While presumably intended to target hacking,
% the \acs{CFAA} has been used to prosecute a host of crimes, and suffers from dated language;
% % ---what does it mean to ``access'' a ``computer'' loading a simple webpage may involve dozens of devices---
% whether violating the terms of service constitutes ``exceeding authorized access'' remains an open question
% \cite{wolff_computer_2016}. Importantly for \ac{EA}, the law includes carve-outs for law enforcement and intelligence
% activities.
%
% Follow up: CFAA going before supreme court: https://www.cyberscoop.com/cfaa-will-soon-day-supreme-court/
% }

    \law{1986}{\acf{ECPA}}{\cite{kastenmeier_hr4952_1986}}{

@@

    \law{1994}{\acf{CALEA}}{\cite{edwards_hr4922_1994}}{

@@

    \law{2001}{\ac{USAPATRIOTAct}}{\cite{sensenbrenner_2001}}{

@@

%     \law{2007}{\acf{PAA}}{\cite{mcconnell_s1927_2007}}{
% Retroactively approved of George W. Bush's warrantless wiretapping policy, a loose interpretation of FISA
% \cite{landau_making_2013}.
% }

    \law{2008}{\acf{FISAAA}}{\cite{reyes_hr6304_2008}}{

@@

    \law{2015}{\ac{USAFREEDOMAct}}{\cite{sensenbrenner_2015}}{

@@

    \law{1993}{The \ac{clipperchip}}{\cite{press_1993}}{

@@

    \law{1996}{The \acf{SAFEAct}}{\cite{goodlatte_hr3011_1996}}{

@@

    \law{1996}{The \acf{PROCODEAct}}{\cite{burns_s1726_1996}}{

@@

%     \law{1997}{Encrypted Communications Privacy Act}{\cite{leahy_s376_1997}}{
% % mix of SE protection and EA guidelines?
% }

%     \law{1998}{Encryption Protects the Rights of Individuals from Violation and Abuse in CYberspace (E-PRIVACY) Act}
%         {\cite{ashcroft_s2067_1998}}{
% % like above?
% }

%     \law{1999}{Encryption for the National Interest Act}{\cite{goss_hr2616_1999}}{
% }

%     \law{1999}{Tax Relief for Responsible Encryption Act}{\cite{goss_hr2617_1999}}{
% % ^^ these two introduced by same rep on same day
% }

    \law{1999}{\ac{CESA}}{\cite{administration_CESA_1999}}{

@@

    \law{2000}{Enhancement of Privacy and Public Safety in Cyberspace Act}{\cite{leahy_s3083_2000}}{

@@

    \law{2016}{Compliance with Court Orders Act (discussion draft)}{\cite{burr_2016}}{

@@

    \law{2018}{The Secure Data Act}{\cite{lofgren_hr5823_2018}}{

@@

    \law{2019}{The \ac{ENCRYPTAct}}{\cite{lieu_hr4170_2019}}{

@@

    \law{2020}{The \acf{EARNITAct}}{\cite{graham_s3398_2020}}{

@@

    \law{2020}{The \acf{LEADAct}}{\cite{graham_2020}}{

@@

% IDEA: put this in an appendix too? Or its own chapter? Too much detail for the background section.
%
% For more, read donahue_comparative_2018 (Israel and China) and \cite{budish_encryption_2018} (framework for analysis)
%
% Since the enactment of the Regulation of Investigatory Powers Act 2000, the U.K. government had the ability to serve
% written notices requiring mandated decryption. Law enforcement and intelligence agencies also have explicit permission
% to perform ``computer network exploitation,'' and approach this thesis refers to as ``\ac{lawful-hacking}.'' 2016's
% Investigatory Powers Act expanded these capabilities and, among other additions, in section 253 created ``technical
% capability notices'' that the Secretary of State can issue to telecommunications operators mandating \ac{EA}
% \cite{legislature_2016}.

@@

% There are several types of approaches:
% IDEA: my selections here are also rather sparse. Create another appendix? (I love work). Possibly create table of
% properties below, similar to denning_taxonomy_1996. savage_lawful_2018 has some good citations to mine.
% - Allow strong encryption (anyone with the users' private keys can see it)
% - Disallow encryption (anyone can see it)
% - Make encryption sufficiently weak, e.g. limit key length (anyone with enough CPU can see it)
% - Require use of backdoor-ed algorithms, security via obscurity (anyone with the secret knowledge can see it)
% - Allow any encryption, just be able to provide keys (anyone with the extra keys can see it)
%   - Store extra in govt DBs, in corporate DBs, in third-party DBs, on blockchain, in secure HW on device
%   - Split the key and store it multiple places
%   - See denning_taxonomy_1996
% - Use some alternative path
%   - Coerced passwords, finding unencrypted copies, seizing devices while unlocked, lawful hacking

@@

% Moving forward, what are the elements that are needed for a feasible EA system? (1) White-box-secure ways of producing
% key recovery information. Do the protocols exist? EES failed. Needs to be rock solid. (2) Dispersed key recovery
% information. (3) A robust, anti-fragile, inherently secure means of protecting those keys, and perhaps decaying them
% over time (https://en.wikipedia.org/wiki/Data_degradation).

@@

\subsection{Non-Escrow Cryptographic Data Recovery}

@@

% these look good: \cite{sacharoff_unlocking_2018}, \cite{fredona_fifth_2016}
% this probably has something to say: kerr_encryption_2017

@@

% FIXME: Separate out into separate, short chapter. Also adds natural place to introduce my more "advanced" DFD syntax.

% Kalafut: I'm not sure that 2.5 and 2.6 really fit well as subsections of 2. Consider separating them into their own
% (short) chapter.
% Kalafut: Argument maps are used in chapter 4. I'm not sure that you need to mention argdown at all. If you do, I would
% only do so in the context of stating that it is the tool you are using to create argument maps.

@@

### 2020-11-20 Thesis-Chapter3-PolicyMaking.tex
Address review feedback

The more important insight is one step removed: precisely because there is an inexhaustable set of potential solutions,
the problem definition---that is, the set of information required to produce a solution---is not self-contained. Each
proposed solution demands research and context to be added to the problem definition. This feedback from proposal to
definition violates the linearity of the traditional approach. One cannot reason from problem statement to proposals to
a solution; instead, one is forced to constantly refine the problem statement based on the content of proposals
themselves.

@@

\begin{enumerate}
  \item There is no formulation that encapsulates the problem of encryption's interplay with privacy, security,
        safety, and trust.
  \item Balancing each value in the face of constantly evolving technology is never ending.
  \item \ac{EA} or other proposals cannot definitively solve the problem.
  \item \ac{EA} or other proposals cannot be objectively tested.
  \item Every policy implementation has irreversible effects.
  \item There is an inexhaustable set of potential solutions to the problem.
  \item Solutions from other domains do not apply directly to this problem.
  \item The need for \ac{EA} or some alternative is a symptom of differing values, rapid technological change, and
        criminal behavior.
  \item The problem can be framed as insufficient investigatory access to digital data (presupposing \ac{EA} as the
        solution), outdated cyberlaw (presupposing legal hacking or compelled password disclosure as solutions), and
        more.
  \item The decisions of regulators and technologists alike have real impacts in the world today.
\end{enumerate}

@@

% So should I follow my own advice and focus on
%   group_2019 (argues for DAR) and
%   savage_lawful_2018 (a concrete DAR proposal)? -- and related, servan_schreiber_jje_2020

@@

% Note on using argument maps to facilitate this argumentative process

@@

% Summarize chapter: wicked problems, why normal methods fail, how this strategy works

@@

In the context of \ac{encryption} and \ac{EA}, this means that the outcome of \ac{the-cw1} doesn't hold precedential
power over the debate in the second. It means that re-raising questions about the role of technology is playing society
is legitimate. To follow this proposed strategy would mean that hardline rhetoric doesn't help \cite{ruiz_there_2018}
\cite{geller_2019}, though sincere appeals do \cite{abelson_2015} \cite{intl_2020} \cite{rozenshtein_2019}. Even more
helpful are collaborative efforts involving government, technical, and civil liberties representatives
\cite{committee_decrypting_2018} \cite{group_2019}. Specific proposals around which groups can center discussion,
whether they specify a particular form of \ac{EA} or perhaps especially if they don't, are also a necessary component
\cite{kerr_encryption_2017} \cite{wright_crypto_2018} \cite{phan_key_2017}.

>>>>

The more important insight is one step removed: precisely because there is an inexhaustible set of potential solutions,
the problem definition---that is, the set of information required to produce a solution---is not self-contained. Each
proposed solution demands research and context to be added to the problem definition. This feedback from proposal to
definition violates the linearity of the traditional approach. One cannot reason from problem statement to proposals to
a solution; instead, one is forced to constantly refine the problem statement based on the content of proposals
themselves.

@@

\begin{enumerate}
  \item There is no formulation that encapsulates the problem of encryption's interplay with privacy, security,
        safety, and trust.
  \item Balancing each value in the face of constantly evolving technology is never ending.
  \item \ac{EA} or other proposals cannot definitively solve the problem.
  \item \ac{EA} or other proposals cannot be objectively tested.
  \item Every policy implementation has irreversible effects.
  \item There is an inexhaustible set of potential solutions to the problem.
  \item Solutions from other domains do not apply directly to this problem.
  \item The need for \ac{EA} or some alternative is a symptom of differing values, rapid technological change, and
        criminal behavior.
  \item The problem can be framed as insufficient investigatory access to digital data (presupposing \ac{EA} as the
        solution), outdated cyberlaw (presupposing legal hacking or compelled password disclosure as solutions), and
        more.
  \item The decisions of regulators and technologists alike have real impacts in the world today.
\end{enumerate}

@@

% So should I follow my own advice and focus on
%   group_2019 (argues for DAR) and
%   savage_lawful_2018 (a concrete DAR proposal)? -- and related, \cite{servan_schreiber_jje_2020}

@@

@@

% TODO: Kalafut: It's not clear to me that this paragraph is a good fit here. It is good content. Perhaps this paragraph
% or its ideas should be at the start of the Argument Maps section.

@@

In the context of \ac{encryption} and \ac{EA}, this means that the outcome of \ac{the-cw1} doesn't hold precedential
power over the debate in the second. It means that re-raising questions about the role of technology is playing society
is legitimate. To follow this proposed strategy would mean that hard-line rhetoric doesn't help \cite{ruiz_there_2018}
\cite{geller_2019}, though sincere appeals do \cite{abelson_2015} \cite{intl_2020} \cite{rozenshtein_2019}. Even more
helpful are collaborative efforts involving government, technical, and civil liberties representatives
\cite{committee_decrypting_2018} \cite{group_2019}. Specific proposals around which groups can center discussion,
whether they specify a particular form of \ac{EA} or perhaps especially if they don't, are also a necessary component
\cite{kerr_encryption_2017} \cite{wright_crypto_2018} \cite{phan_key_2017}.

### 2020-11-20 Thesis-Chapter4-Arguments.tex
Address review feedback

\chapter{EA Debate Argument Maps}
\label{chap-arguments}

@@

A significant portion of the disconnect between government and technical community representatives is disagreement over
whether law enforcement has \ii{too little} or \ii{too much} access to data. The argument for \ii{too little} is
well-represented by proponent former \ac{FBI} Director James Comey in a 2014 speech \cite{comey_2014} (though he did not
coin the phrase \cite{swire_encryption_2011}). The argument is represented in \myfig{fig-arg-going-dark}, also informed
by critiques \cite{rogaway_moral_2015}.

>>>>

\chapter{EA Debate Arguments}
\label{chap-arguments}

@@

% FIXME: I need to address \cite{koepke_2020} in these maps.

A significant portion of the disconnect between government and technical community representatives is disagreement over
whether law enforcement has \ii{too little} or \ii{too much} access to data. The argument for \ii{too little} is
well-represented by proponent former \ac{FBI} Director James Comey in a 2014 speech titled ``Going Dark''
\cite{comey_2014} (though he did not coin the phrase \cite{swire_encryption_2011}). The argument is represented in
\myfig{fig-arg-going-dark}, also informed by critiques \cite{rogaway_moral_2015}.

### 2020-11-20 Thesis-Chapter5-ThreatModel.tex
Address review feedback

\modelitem{The platform abuser}{Why bother with \ac{EA} at all? Because the device user may actually be a threat in the
larger safety context. The end user is not the most important thing. This is a crucial point.

@@

To stray from this rule is dangerous, but---make no mistake---it is already done on a regular basis. Software that can
force updates values the vendor's judgement over the user's (even if it is a good idea). Software that enforces Digital
Rights Management values corporations' rights over the user's (sometimes to extremes \cite{eff_2020}). Software that
doesn't encrypt user communications at all says the service provider's ability to scrape personal information to create
targeted ads is more important than the user's privacy. Software that enables \ac{EA} values lawful investigatory
process over the user's ultimate privacy. Subversion of the user's will is not a pleasant concept, but a spade is a
spade.

In the broader threat model, the platform abuser is someone who is using the device encryption for cover of illicit
activities. They represent a threat to public safety.}

@@

The hawkish lawmaker is a threat to the security of a cryptosystem (\ac{EA} or not) in that they may judge it too
inhibitive to law enforcement and outlaw its very use, mandating something weaker in its place.}

>>>>

\modelitem{The platform abuser}{The device user may actually be a threat in the larger safety context. The end user is
not the most important thing. This is a crucial point.

@@

To stray from this rule is dangerous, but---make no mistake---it is already done on a regular basis. Software that can
force updates values the vendor's judgement over the user's (even if it is a good idea). Software that enforces Digital
Rights Management values corporations' data rights over the user's (sometimes to extremes \cite{eff_2020}). Software
that doesn't encrypt user communications at all values the service provider's ability to scrape personal information to
create targeted ads over the user's privacy. Software that enables \ac{EA} values lawful investigatory process
over the user's ultimate privacy. Intentional subversion of the user's will is not a comfortable thought, but it is a
frequent reality, and the reality of \ac{EA}.

In the broader threat model, the platform abuser is someone who is using the device encryption for cover of illicit
activities. He represents a threat to public safety.}

@@

Hawkish lawmakers are a threat to the security of a cryptosystem (using \ac{EA} or not) in that they may judge it too
inhibitive to law enforcement and outlaw its very use, mandating something weaker in its place.}
